Postdoctoral Fellowship in Astronomy and Planetary Science Research Proposal: \\ The Role of Disk Volatile Chemistry and Dynamics in Shaping the Compositions of Nascent Planets

### 2015-12-11 Postdoc Applications/DTM_proposal.tex
update

%\usepackage{pdfsync}
%\usepackage{subeqnarray}
\usepackage[top=0.9in, bottom=0.8in, left=1in, right=1in]{geometry}
\usepackage{natbib}
\usepackage{color}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage[T1]{fontenc}
\usepackage{titling}
\usepackage{sectsty}
\usepackage{sidecap}
\usepackage{placeins}
\usepackage{indentfirst}
\setlength{\droptitle}{-7em}
\setlength{\abovecaptionskip}{-0.4ex}
\setlength{\belowcaptionskip}{-0.4ex}
%\pagenumbering{gobble}
\pagestyle{fancy}
\lhead{Ana-Maria Piso}
\rhead{ITC Postdoctoral Fellowship Research Proposal}
\date{}
%\rhead{\thepage}

@@

\title{ITC Postdoctoral Fellowship Research Proposal: \\
The Role of Disk Volatile Chemistry and Dynamics in Shaping the Compositions of Nascent Planets}
\author{Ana-Maria Piso}

@@

\textbf{The Institute for Theory and Computation is the ideal place for me to pursue my postdoctoral work.} Its research facilities and academic excellence are incomparable. Even though I am completing my Ph.D. at Harvard, I believe I could continue benefitting as a postdoctoral fellow from the plethora of resources the ITC has to offer, especially given the number of experts in protoplanetary disks and exoplanets that the ITC hosts. As an ITC Fellow, I will have the opportunity to foster new collaborations and thrive as a scientist, both during my postdoctoral tenure and beyond. I would love to collaborate with \textbf{Prof. Dimitar Sasselov}, a world-leading theorist in many aspects of planet formation, atmospheric chemistry and astrobiology. I would also like to work with \textbf{Dr. Matt Holman}, an expert in planetary dynamics. Additionally, both the ITC and the larger CfA research community include leaders in protoplanetary disk observations, such as \textbf{Dr. Sean Andrews} and \textbf{Dr. David Wilner}, as well as distinguished experts in exoplanet detection and characterization, such as \textbf{Prof. Dave Charbonneau} and \textbf{Prof. John Johnson}. Forming such collaborations presents great prospects in connecting my theoretical research work with observations.

@@

\section*{References}
\footnotesize
%\begin{thebibliography} {9}
\noindent $[1]$ Batalha, N. M. 2014, Proceedings of the National Academy of Science, 111, 12647 \\
$[2]$ Lissauer J. J., Dawson R. I., Tremaine S., 2014, Nature, 513, 336 \\
$[3]$ Debes, J. H., Jang-Condell, H., Weinberger, A. J., Roberge, A., \& Schneider, G. 2013, ApJ, 771, 45 \\
$[4]$ Kreidberg, L., Line, M. R., Bean, J. L., et al. 2015, ArXiv e-prints, arXiv:1504.05586 \\
$[5]$ Piso, A.-M. A., \& Youdin, A. N. 2014, ApJ, 786, 21 \\
$[6]$ Piso, A.-M. A., Youdin, A. N., \& Murray-Clay, R. A. 2015, ApJ, 800, 82 \\
$[7]$ Piso, A.-M. A., Öberg, K.I., Birnstiel, T, \& Murray-Clay, R.M., ApJ, resubmitted after referee report \\
$[8]$ ALMA Partnership et al., 2015, ApJ, 808, L3 \\
$[9]$ \"Oberg, K. I., Murray-Clay, R., \& Bergin, E. A. 2011, ApJ, 743, L16 \\
$[10]$ Ida, S., Lin, D. N. C., \& Nagasawa, M. 2013, ApJ, 775, 42 \\
$[11]$ Semenov, D., \& Wiebe, D. 2011, ApJS, 196, 25
%\end{thebibliography}

>>>>

%\usepackage{pdfsync}
%\usepackage{subeqnarray}
\usepackage[top=0.9in, bottom=0.8in, left=1in, right=1in]{geometry}
\usepackage{natbib}
\usepackage{color}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage[T1]{fontenc}
\usepackage{titling}
\usepackage{sectsty}
\usepackage{sidecap}
\usepackage{placeins}
\usepackage{indentfirst}
\setlength{\droptitle}{-7em}
\setlength{\abovecaptionskip}{-0.4ex}
\setlength{\belowcaptionskip}{-0.4ex}
%\pagenumbering{gobble}
\pagestyle{fancy}
\lhead{Ana-Maria Piso}
\rhead{Postdoctoral Fellowship in Astronomy and Planetary Science}
\date{}
%\rhead{\thepage}

@@

\title{Postdoctoral Fellowship in Astronomy and Planetary Science Research Proposal: \\
The Role of Disk Volatile Chemistry and Dynamics in Shaping the Compositions of Nascent Planets}
\author{Ana-Maria Piso}

@@

\textbf{Carnegie DTM is the ideal place for me to pursue my postdoctoral research}, due to is vibrant community of planetary scientists and cosmochemists. I believe that my proposed research lies at the intersection of both these exciting fields, and would mesh well with ongoing research at DTM. In particular, I would love the opportunity to collaborate with \textbf{Dr. Alan Boss} and \textbf{Dr. John Chambers}, world leading planet formation theorists. For the chemical aspect of my proposed project, I would like to collaborate with and learn from \textbf{Dr. Conlel M. O'D. Alexandrer}, an expert in cosmochemistry and the origin of interstellar grains. Additionally, Carnegie DTM hosts leaders in observations of prototplanetary disks and planet formation, such as \textbf{Dr. Alycia Weinberger}. Fostering such collaborations presents great prospects in eventually connecting my theoretical research work with observations.

%\textbf{The Theoretical Astrophysics Center at UC Berkeley is the ideal place for me to pursue my postdoctoral research}, due to its vibrant community of expert theorists in protoplanetary disks and exoplanets. In particular, I would love to collaborate with \textbf{Prof. Eugene Chiang}, a world-leading planet formation theorist. Prof. Chiang's expertise in various topics related to protoplanetary disks and planet dynamics would be instrumental in achieving my research goals during my postdoctoral tenure and afterwards. I would also like to collaborate with \textbf{Prof. Alfred Glassgold}, an expert in protoplanetary disk chemistry. Additionally, the larger UC Berkeley Department of Astronomy hosts leaders in detecting and characterizing worlds outside the Solar system, such as \textbf{Prof. Paul Kalas} and \textbf{Prof. James Graham}, Project Leads of The Gemini Planet Imager Exoplanet Survey. Fostering such collaborations presents great prospects in connecting my
%theoretical research work with observations.

@@

\section*{References}
\footnotesize
%\begin{thebibliography} {9}
\noindent $[1]$ Batalha, N. M. 2014, Proceedings of the National Academy of Science, 111, 12647 \\
$[2]$ Lissauer J. J., Dawson R. I., Tremaine S., 2014, Nature, 513, 336 \\
$[3]$ Debes, J. H., Jang-Condell, H., Weinberger, A. J., Roberge, A., \& Schneider, G. 2013, ApJ, 771, 45 \\
$[4]$ Kreidberg, L., Line, M. R., Bean, J. L., et al. 2015, ArXiv e-prints, arXiv:1504.05586 \\
$[5]$ Piso, A.-M. A., \& Youdin, A. N. 2014, ApJ, 786, 21 \\
$[6]$ Piso, A.-M. A., Youdin, A. N., \& Murray-Clay, R. A. 2015, ApJ, 800, 82 \\
$[7]$ Piso, A.-M. A., Öberg, K.I., Birnstiel, T, \& Murray-Clay, R.M., ApJ, accepted, arXiv:1511.05563 \\
$[8]$ ALMA Partnership et al., 2015, ApJ, 808, L3 \\
$[9]$ \"Oberg, K. I., Murray-Clay, R., \& Bergin, E. A. 2011, ApJ, 743, L16 \\
$[10]$ Ida, S., Lin, D. N. C., \& Nagasawa, M. 2013, ApJ, 775, 42 \\
$[11]$ Semenov, D., \& Wiebe, D. 2011, ApJS, 196, 25
%\end{thebibliography}
